Accelerating Biomolecular Nuclear Magnetic Resonance Assignment with A*

### 2014-03-26 paper/tex/Paper.tex
paper stuff

\usepackage{graphicx} %For jpg figure inclusion
\usepackage{times} %For typeface

@@

\section{Introduction}
\label{sub:introduction}

@@

A prerequisite of the assignment process is data collection using experiments that can provide connectivities between neighboring residues. For example, the HNCACB experiment identifies the chemical shifts corresponding to the $C_\alpha$ and $C_{\beta}$ nuclei of one residue (residue $i$), as well as the $C_\alpha$ and $C_{\beta}$ chemical shifts of the immediately preceding residue (residue $i – 1$). In this experiment, the values corresponding to residue $i$ can usually be distinguished from the ($i -1$) values by their higher intensity. However, ambiguities can arise if the intensities are comparable or if the chemical shift values are overlapping. These ambiguities can be resolved by using additional experiments, such as CBCA(CO) NH, which yields the chemical shifts of the preceding residue only. Using all inter-residue connectivities, a chain of correlations through the protein backbone chemical shifts can be established.  This pattern of sequentially linked chemical shift values reflects the sequential linear arrangement of the individual residues in the protein sequence. The pattern is then matched with the protein sequence, by using the fact that certain residues have characteristic $C_\alpha$ and $C_{\beta}$ chemical shift ranges which uniquely identify them. Thus, each measured chemical shift is assigned to a protein residue, and this information can then be used to infer structural information about the biomolecule.

@@

@@

%solution found
A solution has been found once the current best solution's cost is lower than the cost of any nodes in the frontier. The search is then ended. The algorithm then outputs the cost of the best solution followed by the assigned carbon shift values. 
\cite{guntert_automated_2009} \cite{babak_alipanahi_error_2011} \cite{brief_introduction_Poulsen}

@@

>>>>

\usepackage{graphicx} %For jpg figure inclusion
\usepackage{float}
\usepackage{times} %For typeface

@@

\section{Introduction}
\label{sub:introduction}
Knowledge of a protein’s structure allows for further understanding of the function of a protein and alterations to its function that can lead to disease. The post-genomic era has brought the need to gather functional and structural information of unknown proteins that are encoded by newly discovered genes. Through the implementation of Nuclear magnetic resonance (NMR) spectroscopy, the structure of molecules, such as proteins, can be studied. However, NMR spectroscopy generates large amounts of data that needs to be assigned. The assignment process can take months to complete and is prone to error. To allow for major advances in structural biology, a faster and more accurate method needs to be developed. Our research focuses on developing an algorithm to automate the assignment process, in an attempt to minimize human error and accelerate the time consuming task.

@@

A prerequisite of the assignment process is data collection using experiments that can provide connectivities between neighboring residues. For example, the HNCACB experiment identifies the chemical shifts corresponding to the $C_\alpha$ and $C_{\beta}$ nuclei of one residue (residue $i$), as well as the $C_\alpha$ and $C_{\beta}$ chemical shifts of the immediately preceding residue (residue $i -1$). In this experiment, the values corresponding to residue $i$ can usually be distinguished from the ($i -1$) values by their higher intensity. However, ambiguities can arise if the intensities are comparable or if the chemical shift values are overlapping. These ambiguities can be resolved by using additional experiments, such as CBCA(CO) NH, which yields the chemical shifts of the preceding residue only. Using all inter-residue connectivities, a chain of correlations through the protein backbone chemical shifts can be established.  This pattern of sequentially linked chemical shift values reflects the sequential linear arrangement of the individual residues in the protein sequence. The pattern is then matched with the protein sequence, by using the fact that certain residues have characteristic $C_\alpha$ and $C_{\beta}$ chemical shift ranges which uniquely identify them. Thus, each measured chemical shift is assigned to a protein residue, and this information can then be used to infer structural information about the biomolecule.

@@

\begin{figure}[H]
\begin{center}
\includegraphics{carbon}
\end{center}
\caption{aslkfjlkd}
\label{fig:carbon}
\end{figure}

@@

%solution found
A solution has been found once the current best solution's cost is lower than the cost of any nodes in the frontier. The search is then ended. The algorithm then outputs the cost of the best solution followed by the assigned carbon shift values.

@@

\subsection{Future Goals} % (fold)
\label{sub:future_goals}
We are currently looking into the possibility of parallelizing our algorithm. If possible, our algorithm will be able to handle full NMR datasets. We are also looking to use machine learning in order to optimize the cost calculation. 
% subsection future_goals (end)
